Instructions for developing new pages for the MarineOmics webpage

### 2023-12-14 DRAFT_DNA_methylation.Rmd
Update DRAFT_DNA_methylation.Rmd
added bismark summary report code

### Mapping reports

EXAMPLE MAPPING REPORT FROM BISMARK AND HOW TO VISUALIZE IT

@@

# Summary report

>>>>

@@

# Summary Report

Many steps of the Bismark workflow produce reports (.txt files) with useful information (ex. mapping efficiency, percent cytosine methylation, etc.). These files can be collated into processing reports for each individual sample, which can then be further collated into an [HTML summary report](https://gannet.fish.washington.edu/seashell/bu-mox/scrubbed/032120-fds/bismark_summary_report.html):

```
#HTML Processing Report

${bismark_dir}/bismark2report

#Summary Report

${bismark_dir}/bismark2summary
```

These commands should be run in the same directory where all output files are stored.

```{r meth-igv, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/bismark-summary-report.png")
```
